\documentclass{article}

\title{Petrov Day Organizer Guide}
\author{James Babcock (jimrandomh@gmail.com)}
\date{September 26}

\begin{document}

\maketitle

Content note: This event is designed to provoke existential terror and involves
staring into the abyss.

\section{Overview}

Petrov Day is a yearly event on September 26 commemorating the anniversary of
the Petrov incident, where a false alarm in the Soviet early warning system
nearly set off a nuclear war. The purpose of the event is to make catastrophic
and existential risk emotionally salient, by putting it into historical context
and providing positive and negative examples of how it has been handled. This
is not for the faint of heart and not for the uninitiated; it is aimed at those
who already know what catastrophic and existential risk is, have some
background knowledge of what those risks are, and believe (at least on an
abstract level) that preventing those risks from coming to pass is important.

\section{How to Organize}

It's designed for groups of 5-10 people. Because of the participatory elements,
everyone needs to fit at the same table, so if you have more people than that
then you should split into groups, ideally out of earshot of each other. If you
have more people and don't have space to split up comfortably, you might want
to encourage some of them to also hold Petrov Day ceremonies at their own
houses.

Running Petrov Day is pretty easy. You need to invite people over, acquire a
few simple props, and print one copy of the program for each person. You don't
have to write or rehearse anything, and once things get started, you'll be
doing the same things as any other participant. You might want to read through
the program in advance, but this isn't required.

When you invite people to attend, you should also clearly specify the schedule.
Dinner followed by ceremony works well, but make sure the food is all cleared
away before you start. Also, you should warn people not to arrive in the middle.
Here is a sample email you might use to announce that you are hosting Petrov
Day:

\begin{center}
	\parbox{4.5in}{
	Dear friends,\newline
	On September 26th, 1983, the world was nearly destroyed by nuclear war.
	That day is Petrov Day, named for the man who averted it. I will be hosting
	a ritual commemorating the occasion, on September 26th at $\langle$ADDRESS$\rangle$. We
	will gather for dinner at 6:30pm (please bring a dish) and begin the ritual
	at 8pm. It will last for about an hour; please do not arrive in the middle.\newline
	Sincerely,\newline
	$\langle$YOUR NAME$\rangle$}
\end{center}

\section{Materials}
You will need:

\begin{itemize} \itemsep0pt \parskip0pt \parsep0pt
	\item One complete printout of the program for each person
	\item A table with enough chairs to seat everyone
	\item A candle holder
	\item 8 candles and a lighter
	\item A fire extinguisher close enough to retrieve if needed
	\item A deck of small index cards or a pad of post-it notes, and some pens
	\item A decorative bowl to put bits of paper into
\end{itemize}

The candle-holder must hold at least eight candles. A Menorah will work, but it
shouldn't have symbols or iconography from Hanukkah or any other holiday. You
might want to put down aluminum foil to catch dripping wax. Also, make sure you
get candles that won't burn too fast.

There are two versions of the program, one with the pages in order for
single-sided printing, the other with the pages rearranged to print two-sided
and fold in the middle.

\end{document}
